Importance sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-04-16 draft_p2.tex
Finished figure timeseries_extrms_AVG and added it to the paper

Figure~\ref{fig:extreme_avg} displays the timeseries $\{f_d(t^{\star})\}_{t^{\star} \leq t \leq t^{\star}+T}$ for four of the sampled extreme fluctuations sampled in the control timeseries for $F_T$.
It illustrates that the phenomenology of the extreme fluctuations of the time-averaged drag can neither be reduced to case (1) nor case (2). 
Indeed, both cases are featured in figure~\ref{fig:extreme_avg}, along with intermediate cases where the very large value of the drag results from both a very large fluctuation and a large number of typical, however all positive, fluctuations of the instantaneous drag $f_d$.

>>>>

Figure~\ref{fig:extreme_avg} displays the timeseries $\{f_d(t^{\star})\}_{t^{\star} \leq t \leq t^{\star}+T}$ for four of the sampled extreme fluctuations sampled in the control timeseries for $F_T$.
It illustrates that the phenomenology of the extreme fluctuations of the time-averaged drag can neither be reduced to case (1) nor case (2). 
Indeed, both cases are featured in figure~\ref{fig:extreme_avg}, along with intermediate cases where the very large value of the drag results from both a very large fluctuation and a large number of typical, however all positive, fluctuations of the instantaneous drag $f_d$.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{timeseries_extrms_AVG/timeseries_extrms_AVG}
  \caption{Instantaneous drag timeseries corresponding to the highest fluctuations of the time-averaged drag $F_T$ in the control timeseries. The averaging window is $T=10\tau_c$.
  Here $f_d$ denotes the zero-mean, unit variance instantaneous drag. The time-average is normalized by the standard deviation for the time-averaged drag $\sigma_T$.}
  \label{fig:extreme_avg}
\end{figure}
